Tropical Andes plant trait data BIEN

### 2024-05-16 code/L0/L0_TropicalAndes_plants_BIEN_traits.Rmd
update file paths, add date data was downloaded, update data summary to use data_summary function

# Set file paths
```{r}
data_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

@@

# Retrived desired trait data from BIEN

```{r}
BIEN_trait_list()
```

@@

```{r}
print("The number of records is")
nrow(AllDesired_BIEN_plant_traits)
print("The number of species is")
length(unique(AllDesired_BIEN_plant_traits$scrubbed_species_binomial))
print("The number of genera is" )
length(unique(AllDesired_BIEN_plant_traits$scrubbed_genus))
print("The number of families is")
length(unique(AllDesired_BIEN_plant_traits$scrubbed_family))
```

@@

```{r}
print("The number of records is")
nrow(TropicalAndes_BIEN_plant_traits)
print("The number of species is")
length(unique(TropicalAndes_BIEN_plant_traits$scrubbed_species_binomial))
print("The number of genera is" )
length(unique(TropicalAndes_BIEN_plant_traits$scrubbed_genus))
print("The number of families is")
length(unique(TropicalAndes_BIEN_plant_traits$scrubbed_family))
```

>>>>

# Set file paths
```{r}
data_path_L0 <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path_L0 <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

@@

# Retrived desired trait data from BIEN
Data downloaded on 2023-10-25
```{r}
BIEN_trait_list()
```

@@

```{r}
source("~/GitHub/neotropical_plants/code/data_summary.R")

data_summary(AllDesired_BIEN_plant_traits, AllDesired_BIEN_plant_traits$scrubbed_species_binomial, AllDesired_BIEN_plant_traits$scrubbed_genus, AllDesired_BIEN_plant_traits$scrubbed_family)
```

@@

```{r}
source("~/GitHub/neotropical_plants/code/data_summary.R")

data_summary(AllDesired_BIEN_plant_traits, TropicalAndes_BIEN_plant_traits$scrubbed_species_binomial, TropicalAndes_BIEN_plant_traits$scrubbed_genus, TropicalAndes_BIEN_plant_traits$scrubbed_family)
```
